An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-17 paper/paper.tex
paper: minor polish
paper: minor corrections; coh stuff needs work
paper: backend changes to macros for maint; NFC

% Full frame
\newcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}^{#2}}}

@@

% Coherence conditions for frame, layer, and filler: the general macro
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{#1}}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}

% Logical implication
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}

% Some abbreviations
\renewcommand{\D}{\ensuremath{(D)}}
\newcommand{\hdD}{\ensuremath{(D.1)}}
\newcommand{\tlD}{\ensuremath{(D.2)}}
\renewcommand{\d}{\ensuremath{(d)}}
\newcommand{\E}{\ensuremath{(E)}}
\renewcommand{\l}{\ensuremath{(l)}}
\renewcommand{\c}{\ensuremath{(c)}}

@@

\section{Trunacated $n$-sets}
In this section, we give the core of the definition of truncated $n$-sets
as a coinductive limit.

% Now, we write the type theory bit, and input the abbreviated tables
% Frame, layer, and filler
\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][#2][#3][#4]}
\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}

% Restriction for frame, layer, and filler
\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][][#4][#5][#6]}
\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][][#4][#5][#6]}

% Coherence conditions for frame, layer, and filler
\newcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][#2][#3][][][][][#8]}
\newcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
\newcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}

The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}. It describes the structure of the underlying higher-dimensional relations on which fillers are built. Note the presence of a coherence condition $\cohframe[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type. The proof of $\cohframe[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}. Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory). Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohframe[l]$ anymore.

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][][][#4][#5][][#7][#8]}
\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[][][][#4][#5][][#7][#8]}
\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[][][][#4][#5][][#7][#8]}

@@

\newpage
\appendix
\section{Tables in full detail}
% Frame, layer, and filler
\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}

\renewcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}_{#1}^{#2}}}

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}

>>>>

@@

% Coherence conditions for frame, layer, and filler: the general macro
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}, \joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{(D)}}
\newcommand{\hdD}{\ensuremath{(D.1)}}
\newcommand{\tlD}{\ensuremath{(D.2)}}
\renewcommand{\d}{\ensuremath{(d)}}
\newcommand{\E}{\ensuremath{(E)}}
\renewcommand{\l}{\ensuremath{(l)}}
\renewcommand{\c}{\ensuremath{(c)}}

@@

\section{Trunacated \texorpdfstring{$n$}{n}-sets}
In this section, we give the core of the definition of truncated $n$-sets
as a coinductive limit.

% Now, we write the type theory bit, and input the abbreviated tables
% Frame, layer, and filler
\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][#2][#3][#4]}
\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}
\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
% Restriction for frame, layer, and filler
\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][][#4][#5][#6]}
\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][][#4][#5][#6]}

% Coherence conditions for frame, layer, and filler
\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][][][#8]}
\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][][][#8]}
\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][][][#8]}

The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}. It describes the structure of the underlying higher-dimensional relations on which fillers are built. Note the presence of a coherence condition $\cohf[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type. The proof of $\cohf[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}. Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory). Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohf[l]$ anymore.

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][][#7][#8]}
\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][][#7][#8]}
\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][][#7][#8]}

@@

\newpage
\appendix
\section{Tables in full detail}
% Frame, layer, and filler
\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}

@@

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
